|

### 2025-03-19 manuscript.Rmd
Updated readme with citation information

---
title: |
  | Neural correlates of the uncanny valley effect
  | for robots and hyper-realistic masks 
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document: default
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: plos.csl
author: |
  | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$,
  | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$
---

>>>>

---
title: |
  | Neural correlates of the uncanny valley effect
  | for robots and hyper-realistic masks 
output:
  word_document: default
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  pdf_document:
    toc: no
  html_document: default
bibliography: references.bib
csl: plos.csl
author: |
  | Shona Fitzpatrick$^1$, Ailish K. Byrne$^2$, Alex Headley$^1$, Jet G. Sanders$^3$,
  | Helen Petrie$^4$, Rob Jenkins$^1$ & Daniel H. Baker$^{1,5}$
---
